TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2016-12-05 ISORC2016/paper.tex
Update text

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\cite{par:mruby}

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Conclusion}
The conclusion goes here.

@@

The authors would like to thank...

>>>>

% Package List
%\usepackage[dvips]{graphics}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
% \author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
% Homer Simpson\IEEEauthorrefmark{2},
% James Kirk\IEEEauthorrefmark{3}, 
% Montgomery Scott\IEEEauthorrefmark{3} and
% Eldon Tyrell\IEEEauthorrefmark{4}}
% \IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
% Georgia Institute of Technology,
% Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
% \IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
% Email: homer@thesimpsons.com}
% \IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
% Telephone: (800) 555--1212, Fax: (888) 555--1212}
% \IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}

Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.

TINET is a TCP/IP protocol stack for embedded systems.
TINET is a compact TCP/IP protocol stack, however consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.

To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and add/remove TCP (or UDP) function.
We evaluate the component-based TINET compared with the original TINET, and confirm that the overheads of execution time and memory consumption are low and  that the configurability is improved.

In this paper, we also demonstrates a use case of the dynamic component connection method of TECS with a network application.

\end{abstract}

@@

\section{Introduction}
\label{sec:Introduction}

Internet of Things (IoT) is an essential keyword for the next era.
Such as wearable devices, smart devices, and smart homes, various things are connected to the Internet, enriching our lives.
Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
Therefore, embedded network software is required for the high productivity and quality.

TINET (Tomakomai InterNETworking) \cite{url:TINET} is a compact TCP/IP protocol stack for embedded systems.
TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
However, there are several issues that TINET consists of many complex source codes.
It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET.

{\bf Contributions:} This paper provides the following contributions.

\begin{enumerate}

    \item {\bf Improve configurability}

    \item {\bf Dynamic connection method}

    \item {\bf Support legacy codes}

    % \item {\bf Software visualization}

\end{enumerate}

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:Basic Technology} introduces the basic technologies, i.e., TINET and TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation and Demonstration} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

\section{Basic Technology}
\label{sec:Basic Technology}

\subsection{TINET}

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS project.
To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

\begin{enumerate}
    \item Minimum copy frequency
    \item Elimination of dynamic memory control
    \item Asynchronous interface
    \item Error detailed per API
\end{enumerate}

TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.

\subsubsection{Overview}

Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
    \caption{Hierarchy Diagram of TINET and TOPPERS/ASP3}
    \label{fig:TINET_Hier}
\end{figure}

\subsection{TECS}
\label{sec:TECS}

TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

In TECS, component deployment and composition are performed statically.
Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/component_diagram.eps}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}

Fig.\ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

\subsubsection{Component Description}

In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees,
               [in] uint32_t speed_abs,
                [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

\end{description}

\section{Design and Implementation}
\label{sec:Design and Implementation}

\subsection{TECS Adapter}

TECS supports {\it Adapter} functionality which enables to call a function in TECS from C codes.
An adapter connects a TECS component, links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
Software developers can utilize an existing application for TECS owing to the adapter.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/TECS_Adapter.pdf}
    \caption{TECS Adapter}
    \label{fig:TECS_Adapter}
\end{figure}

\section{Evaluation and Demonstration}
\label{sec:Evaluation and Demonstration}

\begin{table}[t]
    \centering
    \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:Evaluation_Board_Environment}
\end{table}

\section{Related Work}
\label{sec:Related Work}

\section{Conclusion}
\label{sec:Conclusion}

@@
